Comparison between baseline and test performance

### 2022-10-06 analysis/baseline.Rmd
shortened labelling process
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r file, include = FALSE}
data_ioi = "preprocessor/trimmed/dt_ioi_trimmed.txt"
data_kot = "preprocessor/trimmed/dt_kot_trimmed.txt"
data_vel = "preprocessor/trimmed/dt_vel_trimmed.txt"
data_vel_diff = "preprocessor/trimmed/dt_vel_diff_trimmed.txt"
data_baseline_ioi = "preprocessor/predata/trimmed/dt_ioi_trimmed.txt"
data_baseline_kot = "preprocessor/predata/trimmed/dt_kot_trimmed.txt"
data_baseline_vel = "preprocessor/predata/trimmed/dt_vel_trimmed.txt"
data_baseline_vel_diff = "preprocessor/predata/trimmed/dt_vel_diff_trimmed.txt"
```

```{r prep, include = FALSE}
dt_ioi <- fread(data_ioi, header = T, sep = ",", dec = ".")
dt_kot <- fread(data_kot, header = T, sep = ",", dec = ".")
dt_vel <- fread(data_vel, header = T, sep = ",", dec = ".")
dt_vel_diff <- fread(data_vel_diff, header = T, sep = ",", dec = ".")

# SubNr as a factor
dt_ioi$SubNr <- as.factor(dt_ioi$SubNr)

# assign stimuli categories
dt_ioi$Stimuli <- as.numeric(gsub(".mid", "", dt_ioi$Stimuli))
dt_ioi$Articulation <- "NA"
dt_ioi$Dynamics <- "NA"
dt_ioi$Category <- "NA"
dt_ioi[Stimuli < 5]$Articulation <- "Present"
dt_ioi[Stimuli < 5]$Dynamics <- "Absent"
dt_ioi[Stimuli < 5]$Category <- "art_only"
dt_ioi[Stimuli > 4 & Stimuli < 9]$Articulation <- "Absent"
dt_ioi[Stimuli > 4 & Stimuli < 9]$Dynamics <- "Present"
dt_ioi[Stimuli > 4 & Stimuli < 9]$Category <- "dyn_only"
dt_ioi[Stimuli > 8 & Stimuli < 13]$Articulation <- "Present"
dt_ioi[Stimuli > 8 & Stimuli < 13]$Dynamics <- "Present"
dt_ioi[Stimuli > 8 & Stimuli < 13]$Category <- "both"
dt_ioi[Stimuli > 12]$Articulation <- "Absent"
dt_ioi[Stimuli > 12]$Dynamics <- "Absent"
dt_ioi[Stimuli > 12]$Category <- "none"

dt_kot$Stimuli <- as.numeric(gsub(".mid", "", dt_kot$Stimuli))
dt_kot$Articulation <- "NA"
dt_kot$Dynamics <- "NA"
dt_kot$Category <- "NA"
dt_kot[Stimuli < 5]$Articulation <- "Present"
dt_kot[Stimuli < 5]$Dynamics <- "Absent"
dt_kot[Stimuli < 5]$Category <- "art_only"
dt_kot[Stimuli > 4 & Stimuli < 9]$Articulation <- "Absent"
dt_kot[Stimuli > 4 & Stimuli < 9]$Dynamics <- "Present"
dt_kot[Stimuli > 4 & Stimuli < 9]$Category <- "dyn_only"
dt_kot[Stimuli > 8 & Stimuli < 13]$Articulation <- "Present"
dt_kot[Stimuli > 8 & Stimuli < 13]$Dynamics <- "Present"
dt_kot[Stimuli > 8 & Stimuli < 13]$Category <- "both"
dt_kot[Stimuli > 12]$Articulation <- "Absent"
dt_kot[Stimuli > 12]$Dynamics <- "Absent"
dt_kot[Stimuli > 12]$Category <- "none"

dt_vel$Stimuli <- as.numeric(gsub(".mid", "", dt_vel$Stimuli))
dt_vel$Articulation <- "NA"
dt_vel$Dynamics <- "NA"
dt_vel$Category <- "NA"
dt_vel[Stimuli < 5]$Articulation <- "Present"
dt_vel[Stimuli < 5]$Dynamics <- "Absent"
dt_vel[Stimuli < 5]$Category <- "art_only"
dt_vel[Stimuli > 4 & Stimuli < 9]$Articulation <- "Absent"
dt_vel[Stimuli > 4 & Stimuli < 9]$Dynamics <- "Present"
dt_vel[Stimuli > 4 & Stimuli < 9]$Category <- "dyn_only"
dt_vel[Stimuli > 8 & Stimuli < 13]$Articulation <- "Present"
dt_vel[Stimuli > 8 & Stimuli < 13]$Dynamics <- "Present"
dt_vel[Stimuli > 8 & Stimuli < 13]$Category <- "both"
dt_vel[Stimuli > 12]$Articulation <- "Absent"
dt_vel[Stimuli > 12]$Dynamics <- "Absent"
dt_vel[Stimuli > 12]$Category <- "none"

dt_vel_diff$Stimuli <- as.numeric(gsub(".mid", "", dt_vel_diff$Stimuli))
dt_vel_diff$Articulation <- "NA"
dt_vel_diff$Dynamics <- "NA"
dt_vel_diff$Category <- "NA"
dt_vel_diff[Stimuli < 5]$Articulation <- "Present"
dt_vel_diff[Stimuli < 5]$Dynamics <- "Absent"
dt_vel_diff[Stimuli < 5]$Category <- "art_only"
dt_vel_diff[Stimuli > 4 & Stimuli < 9]$Articulation <- "Absent"
dt_vel_diff[Stimuli > 4 & Stimuli < 9]$Dynamics <- "Present"
dt_vel_diff[Stimuli > 4 & Stimuli < 9]$Category <- "dyn_only"
dt_vel_diff[Stimuli > 8 & Stimuli < 13]$Articulation <- "Present"
dt_vel_diff[Stimuli > 8 & Stimuli < 13]$Dynamics <- "Present"
dt_vel_diff[Stimuli > 8 & Stimuli < 13]$Category <- "both"
dt_vel_diff[Stimuli > 12]$Articulation <- "Absent"
dt_vel_diff[Stimuli > 12]$Dynamics <- "Absent"
dt_vel_diff[Stimuli > 12]$Category <- "none"
```

```{r, include = FALSE}
# combine data with baseline performance
dt_bl_ioi <- fread(data_baseline_ioi, header = T, sep = ",", dec = ".")
dt_bl_kot <- fread(data_baseline_kot, header = T, sep = ",", dec = ".")
dt_bl_vel <- fread(data_baseline_vel, header = T, sep = ",", dec = ".")
dt_bl_vel_diff <- fread(data_baseline_vel_diff, header = T, sep = ",", dec = ".")

dt_bl_ioi$Articulation <- "Baseline"
dt_bl_kot$Articulation <- "Baseline"
dt_bl_vel$Articulation <- "Baseline"
dt_bl_vel_diff$Articulation <- "Baseline"

dt_bl_ioi$Dynamics <- "Baseline"
dt_bl_kot$Dynamics <- "Baseline"
dt_bl_vel$Dynamics <- "Baseline"
dt_bl_vel_diff$Dynamics <- "Baseline"

dt_bl_ioi$Category <- "baseline"
dt_bl_kot$Category <- "baseline"
dt_bl_vel$Category <- "baseline"
dt_bl_vel_diff$Category <- "baseline"

dt_ioi <- rbind(dt_ioi, dt_bl_ioi)
dt_kot <- rbind(dt_kot, dt_bl_kot)
dt_vel <- rbind(dt_vel, dt_bl_vel)
dt_vel_diff <- rbind(dt_vel_diff, dt_bl_vel_diff)
```

>>>>

```{r file, include = FALSE}
data_ioi = "preprocessor/trimmed/dt_ioi_trimmed.txt"
data_kot = "preprocessor/trimmed/dt_kot_trimmed.txt"
data_vel = "preprocessor/trimmed/dt_vel_trimmed.txt"
data_vel_diff = "preprocessor/trimmed/dt_vel_diff_trimmed.txt"
data_bl_ioi = "preprocessor/predata/trimmed/dt_ioi_trimmed.txt"
data_bl_kot = "preprocessor/predata/trimmed/dt_kot_trimmed.txt"
data_bl_vel = "preprocessor/predata/trimmed/dt_vel_trimmed.txt"
data_bl_vel_diff = "preprocessor/predata/trimmed/dt_vel_diff_trimmed.txt"
```

```{r prep, include = FALSE}
# read data
dt_ioi <- fread(data_ioi, header = T, sep = ",", dec = ".")
dt_kot <- fread(data_kot, header = T, sep = ",", dec = ".")
dt_vel <- fread(data_vel, header = T, sep = ",", dec = ".")
dt_vel_diff <- fread(data_vel_diff, header = T, sep = ",", dec = ".")

dt1.list <- list(dt_ioi, dt_kot, dt_vel, dt_vel_diff) # make a list of data tables

# add labels to data tables
label <- function(data){
  data[, "SubNr" := as.factor(data$SubNr)]
  data[, "Stimuli" := as.numeric(gsub(".mid", "", data$Stimuli))]
  data[, c("Articulation", "Dynamics", "Category") := .("NA", "NA", "NA")]
  data[Stimuli < 5, c("Articulation", "Dynamics", "Category") := .("Present", "Absent", "art_only")]
  data[Stimuli > 4 & Stimuli < 9, c("Articulation", "Dynamics", "Category") := .("Absent", "Present", "dyn_only")]
  data[Stimuli > 8 & Stimuli < 13, c("Articulation", "Dynamics", "Category") := .("Present", "Present", "both")]
  data[Stimuli > 12, c("Articulation", "Dynamics", "Category") := .("Absent", "Absent", "none")]
}

# perform the function above
res <- lapply(dt1.list, label)

# read data (baseline performances)
dt_bl_ioi <- fread(data_bl_ioi, header = T, sep = ",", dec = ".")
dt_bl_kot <- fread(data_bl_kot, header = T, sep = ",", dec = ".")
dt_bl_vel <- fread(data_bl_vel, header = T, sep = ",", dec = ".")
dt_bl_vel_diff <- fread(data_bl_vel_diff, header = T, sep = ",", dec = ".")

dt2.list <- list(dt_bl_ioi, dt_bl_kot, dt_bl_vel, dt_bl_vel_diff) # make a list of data tables (baseline performances)

# add labels to data tables
label_bl <- function(data){
  data[, "SubNr" := as.factor(data$SubNr)]
  data[, c("Articulation", "Dynamics", "Category") := .("Baseline", "Baseline", "baseline")]
}

# perform the function above
res_bl <- lapply(dt2.list, label)

# combine data with baseline performance
dt_ioi <- rbind(dt_ioi, dt_bl_ioi)
dt_kot <- rbind(dt_kot, dt_bl_kot)
dt_vel <- rbind(dt_vel, dt_bl_vel)
dt_vel_diff <- rbind(dt_vel_diff, dt_bl_vel_diff)
```
